Modelling RNA-based oscillatory circuits

### 2015-09-16 MScWriteup.tex
final final?

Some aspects of these initial fitting results are worth comment. For example, Fig. \ref{InitialResults_13_9_f} shows that many of the estimated parameter sets in Fig. \ref{InitialResults_13_9_hist} do not give the minimum error function value found - instead, the majority find a local minimum slightly above it. In fact, if we examine the estimated parameter sets giving the lowest error values, several have $\mu = 0.05$, the upper bound set. Thus, in the tightly clustered $\mu$ histogram, we must bear in mind that $\mu \approx 0.044$ is not a unique optimum - the error landscape may indeed be pocketed by many local minima, all giving a similar quality of fit.

@@

 There are two main reasons why a parameter may not be estimable \cite{Mclean2012,Yao2003, Beck,Jimenez-Hornero2008,Grewal1976}: Model predictions may be insensitive to the value of a particular parameter, or the effects of varying one parameter on model predictions may be highly correlated with the effects of varying several others. We may begin to investigate these issues in our model by performing a local sensitivity analysis about the solutions found in our initial parameter estimation. We numerically estimate the sensitivity matrix, $S$:

>>>>

Some aspects of these initial fitting results are worth comment. For example, Fig. \ref{InitialResults_13_9_f} shows that many of the estimated parameter sets in Fig. \ref{InitialResults_13_9_hist} do not give the minimum error function value found - instead, the majority find a local minimum slightly above it. In fact, if we examine the estimated parameter sets giving the lowest error values for the \textit{13\_9} dataset, several have $\mu = 0.05$, the upper bound set. Thus, in the tightly clustered $\mu$ histogram, we must bear in mind that $\mu \approx 0.044$ is not a unique optimum - the error landscape may indeed be pocketed by many local minima, all giving a similar quality of fit.

@@

 There are two main reasons why a parameter may not be estimable \cite{Mclean2012,Yao2003, Beck,Jimenez-Hornero2008,Grewal1976}: Model predictions may be insensitive to the value of a particular parameter, or the effects of varying one parameter on model predictions may be highly correlated with the effects of varying several others. We begin to investigate these issues in our model by performing a local sensitivity analysis about the solutions found in our initial parameter estimation. We numerically estimate the sensitivity matrix, $S$ \cite{Mclean2012}:
